%!TEX TS-program = xelatex
%\documentclass[print,a4paper]{friggeri-cv}
%\documentclass[a4paper,printbw]{friggeri-cv}
%\documentclass[a4paper,print]{friggeri-cv}
%\documentclass[a4paper,web]{friggeri-cv}
\documentclass[a4paper]{friggeri-cv}
\addbibresource{aspubs.bib}


% \widowpenalty=1000
% \clubpenalty=1000

\begin{document}
\header{andré}{santos}
       {web, language and semantics}


% In the aside, each new line forces a line break

\begin{aside}
  \section{about}
\begin{sensitive}
    \subsection{address}
    {\small R. Mouzinho de Albuquerque 413,
    hab 3.2
    4450-206 Matosinhos
    Portugal}
    \subsection{phone}
    +351 927 715 379
    \subsection{birth date}
    24 Fev 1988
\end{sensitive}
    \subsection{contacts}
    %\url{andrefs.com}
    \url{github.com/andrefs} \faGithub
    \href{mailto:cv@andrefs.com}{cv@andrefs.com} \faEnvelope
    %\href{http://witter.com/about_andrefs}{@about\_andrefs} \faTwitter
  \section{languages}
    native portuguese
    fluent english
    basic spanish+french
  \section{favorite tools}
    {$\varheartsuit$} TypeScript, React, Docker, Rust
  \section{looking into}
   {\fontspec{Symbola}\symbol{"1F440}} Rust, Kubernetes
\end{aside}

\section{interests}
{Fullstack developer with backend preference, working with
Node.js, React, TypeScript,\\ Docker. Interested in semantic web, natural
language processing, functional programming, machine learning and web development.}

\section{technical skills}

\begin{entrylist}
    \entry
        {Languages}
        {Node.js, TypeScript and Perl}
        {}
        {\small Also Rust, \LaTeX}
        {\vspace{-0.5cm}}
    \entry
        {Databases}
        {MongoDB}
        {}
        {\small Also MySQL, PostgreSQL, ElasticSearch}
        {\vspace{-0.5cm}}
    \entry
    {\parbox[t][][t]{2.3cm}{Frameworks\\{\small and libraries}}}
        {Express, Dancer}
        {}
        {\small Also React, Jest}
        {\vspace{-0.4cm}}
    \entry
        {Other tools}
        {Docker, Git, Bash}
        {}
        {}
        {\vspace{-3.8cm}}
\end{entrylist}

\section{relevant experience}
\begin{entrylist}
  \entry
    {\parbox[t][][t]{1.8cm}{2022 {\footnotesize Jan to}\\2023
    {\footnotesize May}}}
    {Decipad, remote \textendash~\url{decipad.com}}
    {Software engineer}
    {Interactive  notebook to explore data.\footnotesize{Typical tasks
    include:}}
    {\begin{itemize}
      \item improving and extending the grammar for an in-house developed language
      \item implementing logic supporting complex editor components (e.g. code lines)
      \item implementing React components on top of a Slate.js/Plate editor
    \end{itemize}}
  \entry
    {{\tiny since} Apr 2017}
    {INESC TEC, Porto}
    {Research assistant}
    {\vspace{-0.7cm}}
    {}
  \entry
    {\parbox[t][][t]{1.8cm}{2018 {\footnotesize Oct to}\\2020
    {\footnotesize Sep}}}
    {University of Minho, Braga}
    {Guest assistant professor}
    {Teaching MSc classes:}
    {\begin{itemize}
        \item Natural Language Processing
        \item Data Analysis and Visualization
    \end{itemize}
    \url{http://di.uminho.pt}, \url{elach.uminho.pt}
    }
  \entry
    {\parbox[t][][t]{1.8cm}{2016 {\footnotesize Jul to}\\2017 {\footnotesize Mar}}}
    {Contentful GmbH, Berlin \textendash~\url{contentful.com}}
    {JavaScript backend engineer}
    {Headless API-first CMS. \footnotesize{Typical tasks
    included:}}
    {\begin{itemize}
        \item development and support of multiple Node.js APIs,
        \item implementing React components,
        \item writing and debugging PostgreSQL query generators.
    \end{itemize}
    }
  \entry
    {2013--2015}
    {SAPO, Portugal Telecom, Lisbon}
    {Consultant, web developer}
    {Largest Portuguese web portal. \footnotesize{Typical tasks
    included:}}
    {\begin{itemize}
        \item development and support of Node.js APIs,
        \item management of several MongoDB databases,
        \item development of Node.js and Perl frontend websites and backoffices.
    \end{itemize}
    \url{http://sapo.pt}, \url{http://24.sapo.pt}, \url{http://jornais.sapo.pt}
    }
  \entry
    {2011--2013}
    {Subvisual, Braga \textendash~\url{subvisual.co}}
    {Sys admin}
    {UX, UI, web and mobile development company}
    {Typical tasks included:
        \begin{itemize}
            \item deployment and management of Unix-based
            servers, with\\
            Apache and MySQL services, and Ruby on Rails applications
            \item development of helper scripts to automate
            server management tasks
            \end{itemize}
    }
%  \entry
%    {\parbox[t][][t]{1.8cm}{2012 {\footnotesize Nov to}\\2013 {\footnotesize Feb}}}
%    {CEB, University of Minho}
%    {Researcher}
%    {Collective Computation and Control in Complex\\
%    Biochemical Systems. {\footnotesize Activities:}}
%    {
%        \begin{itemize}
%            \item parsing gene expression rules and microarray data
%            \item simulation gene expression
%            \item comparing simulated and experimentally obtained
%                network states
%        \end{itemize}
%    }
%  \entry
%    {\parbox[t][][t]{1.8cm}{2011 {\footnotesize Apr to}\\2012 {\footnotesize Sep}}}
%    {CEHUM, University of Minho}
%    {Researcher}
%    {Project Per-Fide: Portuguese in parallel with six languages:\\
%    Español, Russian, Français, Italiano, Deutsch, English}
%    {See activities description on NLP MSc in \emph{Education}.\\
%    \url{http://per-fide.di.uminho.pt/}}
%  \entry
%    {2009 {\footnotesize Jul-Sep}}
%    {Sapo Summerbits'09}
%    {Research grant}
%    {Open source software development}
%    {\footnotesize
%        Development of natural language processing tools to help in general\\
%        orthography migration challenges, motivated by the 1990 Portuguese\\
%        Language Orthographic Agreement.\\
%        \url{http://natura.di.uminho.pt/wiki/doku.php?id=ferramentas:bigorna}
%    \vspace{-1cm}
%    }
\end{entrylist}

\newpage
\section{education}
\label{education}


\begin{entrylist}
  \entry
    {{\tiny since} Oct 2017}
    {MAP-i Doc. Prog. in Computer Science}
    {Fac. of Sciences of Univ. of Porto, Portugal}
    {\emph{Semantic measures in large semantic graphs (ongoing)}}
    {180 ECTS}
  \entry
    {2011--2012}
    {MSc in Bioinformatics}
    {University of Minho, Portugal}
    {\emph{Mining biological parameters from literature: an\\
    application to environmental decision support systems (thesis)}}
    {Development of a framework
    for building text mining applications\\
    for scientific literature, focused on numerical parameters and\\
    supported by 3rd-party tools and expert-curated
    ontologies.\\
    120 ECTS, final grade 17/20
    }
  \entry
    {2009--2011}
    {MSc in Natural Language Processing}
    {University of Minho, Portugal}
    {\emph{Contributions for building a Corpora-Flow System} (thesis)}
    {\footnotesize{Development of a system to support automatic handling of corpora\\
    (cleaning, validation, format conversion), document alignment and\\
    calculation of alignability metrics of several types of documents.}\\
    120 ECTS, final grade 17/20
    }
  \entry
    {2006--2009}
    {BSc in Software Engineering}
    {University of Minho, Portugal}
    {Typical CompSci course}
    {180 ECTS, final grade 15/20}
\end{entrylist}


% \section{training}
% \begin{entrylist}
%     \entry
%         {2011 {\footnotesize Jul}}
%         {Bang and Olufsen Summer School}
%         {Struer, Denmark}
%         {Conceptual Design and Development of Innovative Products}
%         {\vspace{-0.4cm}}
%     \entry
%         {2010/11}
%         {IdeaLab -- Business Ideas Lab}
%         {TecMinho}
%         {}
%         {\vspace{-0.8cm}}
%     \entry
%         {2010 {\footnotesize Jul}}
%         {Luso-Brazilian Evolutionary Computing School}
%         {University of Minho, Guimarães}
%         {}
%         {\vspace{-0.8cm}}
%     \entry
%         {2010 {\footnotesize Jun}}
%         {Catalyst 5.80}
%         {Portuguese Perl Workshop'10}
%         {\vspace{-0.8cm}}
%         {}
%     \entry
%         {2005 {\footnotesize Set}}
%         {Physics Summer School}
%         {Faculty of Science, University of Porto}
%         {\vspace{-0.8cm}}
%         {}
%     \entry
%         {2005 {\footnotesize Jul}}
%         {German Language Open Course}
%         {Faculty of Arts, Univerity of Porto}
%         {\vspace{-0.8cm}}
%         {}
% \end{entrylist}


\section{other activities}
\subsection{cesium {\normalfont\small University of Minho's Software Engineering Student Center}}{}
\begin{entrylist}
  \entry
    {2009/10}
    {Vice-president}
    {\href{http://cesium.di.uminho.pt}{http://cesium.di.uminho.pt}}
    {\vspace{-.8cm}}
    {}
  \entry
    {2010/11}
    {Director at CAOS}
    {\href{http://caos.di.uminho.pt}{http://caos.di.uminho.pt}}
    {CeSIUM's Open Source Support Center}
    {\vspace{-.5cm}}
\end{entrylist}

\subsection{programming competitions}{}
\begin{entrylist}
  \entry
    {2018}
    {Pixels Camp}
    {\href{https://github.com/luispmiranda/boothchain}{https://github.com/luispmiranda/boothchain}}
    {3rd qualified team with a blockchain-powered photo booth.}
    {\vspace{-.4cm}}
  \entry
    {2015}
    {Miniclip Game Jam}
    {\href{https://github.com/subvisual/planet-mocha}{https://github.com/subvisual/planet-mocha}}
    {3rd qualified and Innovation prize with a space inspired game.}
    {\vspace{-.4cm}}
  \entry
    {2014}
    {SAPO Codebits Hackathon}
    {\href{https://github.com/andrefs/policias\_beduinos}{https://github.com/andrefs/policias\_beduinos}}
    {2nd qualified team with a web application to extract\\
    relevant topics from a large collection of news.}
    {\vspace{-.4cm}}
  \entry
    {2012}
    {APPP Perl Code Sprint}
    {\href{http://perl.pt}{http://perl.pt}}
    {3rd qualified in the Perl programming competition\\organized by the Portuguese Perl Mongers group.}
    {\vspace{-.4cm}}
  \entry
    {2009}
    {Microsoft Imagine Cup'09}
    {Lisbon, Portugal}
    {5$^{\footnotesize\textrm{th}}$~classified in the national finals.}
    {\vspace{-.4cm}}
  \entry
    {2008}
    {ACM South Western European Regional Contests}
    {Nuremberg, Germany}
    {International programming competition.}
    {\vspace{-.4cm}}
  \entry
    {2007-2009}
    {Inter-University Programming Marathon}
    {IST'07, UC'08, ESTGA'09}
    {National ACM-style programming competition.}
    {\vspace{-.4cm}}
\end{entrylist}

\newpage
\subsection{sports}{}
\begin{entrylist}
  \entry
    {{\tiny since} 1999}
    {Judo, 1st Kyu}
    {INATEL, University of Minho, Boavista Futebol Clube, Sport Club
    do Porto}
    %{4$^{\footnotesize\textrm{th}}$~Kyu}
    {\vspace{-.8cm}}
    {}
  \entry
    {2018}
    {Veterans Open Championship}
    {Associação Distrital de Judo de Lisboa}
    {Gold medal}
    {}
  \entry
    {2018}
    {Veterans National Championship}
    {Portuguese Judo Federation}
    {Silver medal}
    {}
  \entry
    {2010-2013}
    {National Judo University Championships}
    {Aveiro'10, Lisbon'11, Aveiro '12, Coimbra '13}
    {\vspace{-.8cm}}
    {}
%  \entry
%    {2007/08}
%    {Basketball}
%    {University of Minho}
%    {\vspace{-.8cm}}
%    {}
%  \entry
%    {1998-2000}
%    {Artistic gymnastics}
%    {INATEL}
%    {}
%    {}
\end{entrylist}


\begin{sloppypar}
%\newpage
\section{publications}
\printbibsection{incollection}{chapter}

\printbibsection{article}{articles in peer-reviewed journal}

\begin{refsection}
  \nocite{*}
  %\printbibliography[type=inproceedings, title={international peer-reviewed conferences/proceedings}, notkeyword={france}, heading=subbibliography]
  \printbibliography[type=inproceedings, title={peer-reviewed conferences/proceedings}, heading=subbibliography]
\end{refsection}

\newpage
\printbibsection{thesis}{dissertations}

\section{presentations and workshops}
\begin{refsection}
  \nocite{*}
  \printbibliography[type=misc, title={presentations}, heading=none]
\end{refsection}
\end{sloppypar}

\end{document}
